Supplementary Materials of Impact of IPTp Regimen on Pregnancy Outcomes

### 2025-05-03 products/manuscript/supplement/Supplementary-Material.qmd
Supp

---
title: "Supplementary Materials of Impact of IPTp Regimen on Pregnancy Outcomes"
format:
  pdf:
    toc: false
    number-sections: true
    highlight-style: github
bibliography:
  - ../../../assets/dataanalysis-references.bib
csl: ../../../assets/american-journal-of-epidemiology.csl
---

@@

# Machine learning & modeling
library(tidymodels)         # Modeling framework (recipes, parsnip, workflows, tune, yardstick, rsample)
library(themis)             # Class-imbalance sampling (e.g., SMOTE)
library(dials)              # Parameter tuning grids
library(ranger)             # Random forest engine
library(xgboost)            # Gradient boosting engine
library(generalhoslem)
library(ResourceSelection)
library(rms)
```

@@

```{r}
# Load necessary libraries
library(dplyr)
library(ggplot2)
library(here)

@@

```{r}
# Load necessary libraries

@@

```{r}
#| label: tbl-resulttable1
#| tbl-cap: "Another fit table."
#| echo: FALSE
resulttable1 = readRDS(here("results","tables","resulttable1.rds"))
knitr::kable(resulttable1)
```

@@

```{r}
#| label: fig-result2
#| fig-cap: "Height and weight."
#| echo: FALSE
knitr::include_graphics(here("results","figures","height-weight.png"))
```

@@

```{r roc-calibration, echo=TRUE, message=FALSE, warning=FALSE}
# 1) Load required libraries
library(dplyr)
library(pROC)
library(caret)
library(here)

@@

# 6) Calibration plot
data_cal <- data.frame(
  observed = factor(promo_data_young$adverse_birth_outcome, levels = c(0,1)),
  predicted = promo_data_young$predicted_prob
)
cal_plot <- calibration(
  observed ~ predicted,
  data  = data_cal,
  class = "1"
)
plot(cal_plot, main = "Calibration Plot: Gravidity Model (Age < 25)")

>>>>

---
title: "Supplementary Materials of Impact of IPTp Regimen on Pregnancy Outcomes"
author: "Asmith Joseph"
format:
  pdf:
    toc: false
    number-sections: true
    highlight-style: github
bibliography:
  - ../../../assets/dataanalysis-references.bib
csl: ../../../assets/american-journal-of-epidemiology.csl
---

@@

# Machine learning & modeling
library(tidymodels)         # Modeling framework (recipes, parsnip, workflows, tune, yardstick, rsample)
library(themis)             # Class-imbalance sampling (e.g., SMOTE)
library(dials)              # Parameter tuning grids
library(ranger)             # Random forest engine
library(xgboost)            # Gradient boosting engine
library(generalhoslem)
library(ResourceSelection)
library(rms)

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold"}
# Load necessary libraries
library(dplyr)
library(ggplot2)
library(here)

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold"}
# Load necessary libraries

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold"}
#| label: tbl-resulttable1
#| tbl-cap: "Another fit table."
#| echo: FALSE
resulttable1 = readRDS(here("results","tables","resulttable1.rds"))
knitr::kable(resulttable1)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold"}
#| label: fig-result2
#| fig-cap: "Height and weight."
#| echo: FALSE
knitr::include_graphics(here("results","figures","height-weight.png"))
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold"}
# 1) Load required libraries
library(dplyr)
library(pROC)
library(caret)
library(here)

@@

# 6) Calibration plot
data_cal <- data.frame(
  observed = factor(promo_data_young$adverse_birth_outcome, levels = c(0,1)),
  predicted = promo_data_young$predicted_prob
)
cal_plot <- calibration(
  observed ~ predicted,
  data  = data_cal,
  class = "1"
)
plot(cal_plot, main = "Calibration Plot: Gravidity Model (Age < 25)")
```
